### 2022-01-27 article.tex
More attribution!

  \item We evaluate match types in a case study, presenting a type-safe version of the NumPy library (\Cref{sec:evaluation}).

@@

\section{Case Study: Shape-Safe NumPy}
\label{sec:evaluation}

>>>>

  \item We evaluate match types in a case study, presenting a type-safe version of the NumPy library (\Cref{sec:case-study-shape-safe-num-py}).

@@

\section{Case Study: Shape-Safe NumPy}
\label{sec:case-study-shape-safe-num-py}
